%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD researcher, Advisor: John-Stephen Taylor} % Job title
    {Washington University in St. Louis} % Organization
    {St. Louis, USA} % Location
    {2012 - PRESENT} % Date(s)
    {
    \begin{cvitems}
    \item {Thesis: Effect of DNA sequence context, DNA structure, and excitation method on cyclobutane pyrimidine dimer (CPD) formation for illustrating epigenetics mechanism underlying skin cancers.}
    \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Graduate Teaching Assistant} % Job title
    {Washington University in St. Louis} % Organization
    {St. Louis, USA} % Location
    {2012 - 2015} % Date(s)
     {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Independently taught General Chemistry Lab I and II(5 semesters, 6 lab sections, 110 students).}
        \item {Grader for CSE584A, Algorithm for Biosequence Matching}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Consultant} % Job title
    {BALSA} % Organization
    {St. Louis, USA} % Location
    {2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Performed market sizing and competitive analysis for local biotech and life science companies.}
        \item {Worked and communicated with team, and reported and presented results weekly.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher, Advisor: Shikuo Li} % Job title
    {Anhui University} % Organization
    {Hefei, China} % Location
    {2010 - 2012} % Date(s)
      {
    \begin{cvitems}
    \item {Thesis: One pot synthesis of Cu2O-Graphene hydrogel for its application in electrochemistry}
    \end{cvitems}
    }
%---------------------------------------------------------
 \end{cventries}