%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  	{\url{https://github.com/lvchen727/udacity-machine-learning}} % Role
    {Machine Learning Projects}% Event
    {Udacity} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Developed a decision tree model to predict the value of a given house in the Boston real estate market and identified the best selling price for the customers using statistical analysis tools.}
        \item {Trained and tested supervised machine learning models(SVM, Decision Tree, Naive Bayes) on a given dataset to test the factors that affect a student's performance in high school. }
        \item {Successfully employed unsupervised learning algorithms (Gaussian Mixture Model) to build customer segments from unstructured data with the help of PCA to reduce the data dimensionality.}
        \item {Applied reinforcement learning(Q-learning) to build a simulated vehicle navigation agent to drop off the passenger to the goal state in the shortest time possible. }
      \end{cvitems}
    }

%---------------------------------------------------------
 \cventry
  	{\url{https://github.com/lvchen727/Algorithms-for-Biosequencing-Comparison}} % Role
    {K-mer Kernels}% Event
    {WashU CSE584A Final Project} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Wrote python scripts to process raw next generation sequencing data.}
        \item {Implemented the linear-time DC3 suffix array construction algorithm to build 2BWT in JAVA.}
        \item {Developed 2BWT-based algorithm to construct distance table by counting unique k-mers in genomes. }
        \item {Successfully generated the phylogeny tree for 4 real genomes through built program.}
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
  	{\url{https://github.com/lvchen727/Algorithms-for-Computational-Biology}} % Role
    {Computational Biology}% Event
    {WashU CSE587A Course Projects} % Location
    {2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Implemented MEME algorithm for finding multiple motifs in biopolymers.}
        \item{Implemented the Viterbi algorithm for HMM decoding. }
        \item{Implemented Baum-Welch algorithm for unsupervised parameter estimation.}
        \item{Implemented the Smith-Waterman algorithm for local alignment of two DNA sequences.}
      \end{cvitems}
    }
%---------------------------------------------------------
 \cventry
  	{\url{https://github.com/lvchen727/Algorithms-and-Data-Structures}} % Role
    {Algorithms and Data Structures}% Event
    {WashU CSE502N Course Projects} % Location
    {2015} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item{Implemented the divide-and-conquer algorithm to find the closest pair of points in the inputs.}
        \item{Implemented hashing as part of a tool for comparing genomic DNA sequences. }
        \item{Implemented skip list as a database indexing strategy to achieve quick queries.}
      \end{cvitems}
    }
%---------------------------------------------------------


\end{cventries}
